Hedonic House Prisce Model King County

### 2023-11-19 Msb205/Msb205.qmd
:(
;-)

```{r}
mod1 <- KC_husdata "price ~ bedrooms + bathrooms + sqft_living + sqft_living15 + sqft_lot + sqft_lot15 + sqft_above + floors + grade + yr_built + yr_renovated + waterfront + condition + view + dist_cbd_km + EHD_percen + low + high + year_month"
```

>>>>

```{r}
model <- lm(price ~ bedrooms + bathrooms + sqft_living + sqft_living15 + sqft_lot + sqft_lot15 + sqft_above + floors + grade + yr_built + yr_renovated + waterfront + condition + view + dist_cbd_km + EHD_percen + low + high + year_month, data = KC_husdata)

# Print a summary of the model
summary(model)
